---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# WiGISKeDataViz3

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/anelda/WiGISKeDataViz3.svg?branch=master)](https://travis-ci.org/anelda/WiGISKeDataViz3)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/anelda/WiGISKeDataViz3?branch=master&svg=true)](https://ci.appveyor.com/project/anelda/WiGISKeDataViz3)
[![Codecov test coverage](https://codecov.io/gh/anelda/WiGISKeDataViz3/branch/master/graph/badge.svg)](https://codecov.io/gh/anelda/WiGISKeDataViz3?branch=master)
<!-- badges: end -->

The goal of WiGISKeDataViz3 is to facilitate easy access to datasets, analysis and visualisation used in the Women in GIS Kenya data viz challenge #3 where the focus was on teenage pregnancies between 2016 - 2020. For more information about the challenge see https://wigis.co.ke/project/visualizing-teenage-pregnancy-and-related-factors/.

## Installation

WiGISKeDataViz3 is not on CRAN but you can install the development version available on Github as follows:

``` {r}
# install.packages("devtools") # if not already installed

devtools::install_github("afrimapr/WiGISKeDataViz3")

```

## Example

Access population data from the World Bank Data Bank to normalise pregnancy data. The World Pop datasets that will work (given the dataformat and cleanup code) include "SP.POP.1014.FE", "SP.POP.1014.MA", "SP.POP.1519.FE", "SP.POP.1519.MA".

```{r example}
library(WiGISKeDataViz3)

## Obtaining population data for females from Kenya ages 10 - 14 for the years 2016 - 2019
ken_fem_1014 <- get_wb_gender_age_pop_data(country_iso = "KEN", indicator_code = "SP.POP.1014.FE", start = 2016, end = 2019, new_date = 2020)

```

